Individual Stellar Halos of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-10-16 draft/paper1_v14.tex
For referee report

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\rachel}[1]{\textcolor{cyan}{\textbf{[Rachel: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

    Massive galaxies display extended light profiles that can reach several 
    hundreds of kilo parsecs. 
    These stellar halos provide a fossil record of galaxy assembly histories. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which enables us to individually 
    estimate surface mass density profiles to 100 kpc without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles.  
    When this extended light is not properly accounted for as a result of shallow imaging 
    or inadequate profile modeling, the derived stellar mass function can be 
    significantly underestimated at the highest masses.  
    Across our sample, the ellipticity of outer light profiles increases substantially 
    as we probe larger radii.  
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at late times from a series of merging events. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the depth and imaging quality of SDSS and the HSC wide 
            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
            This added depth is critical in order map the outskirts of ETGs out to 
            large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    population of massive quiescent galaxies at high redshift that have smaller 
    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
    vanDokkum2008, Cimatti2008}).  
    These high redshift galaxies also have slightly higher central velocity dispersions 
    and stellar mass densities (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), 
    and more disk-like morphologies (e.g. \citealt{vanderWel2011}) than low redshift 
    galaxies (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar mass.

    Following the initial phase of growth, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors are already quiescent by $z=1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    The ``two-phase'' formation of massive galaxies help explain both the 
    observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies 
    (e.g. \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
    halos  (e.g. \citealt{Szomoru2012, Patel2013}). 
    It also posits that minor mergers dominate the mass assembly 
    of massive galaxies at late times 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).

    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total galaxy stellar 
    mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    For instance, recent results from the 
    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at 
    \logms{}$>11.5$ (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
    does not reproduce the observed stellar mass function at high \mstar{} end.}. 
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront this model with additional observations, 
    in particular, the detailed surface mass density profiles of low redshift massive 
    galaxies. 
    Early studies based on one-dimensional light profiles found that the surface 
    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
    (e.g. \citealt{Kormendy2009}; except for the most central region) and that the 
    \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). 
    However, recently, detailed empirical comparison of surface brightness profiles 
    revealed a more complicated situation showing that ETGs belong to two families, 
    those that follow single-\ser{} law, versus those that significantly deviate from 
    the single-\ser{} profile \citep{Schombert2015}.  
    Two-dimensional analyses have also found that the stellar distributions of massive 
    ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  
    \citet{Huang2013b} further suggest a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and 
    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).

    Until now, studies of the surface brightness or mass density profiles of massive 
    galaxies have been either conducted using large samples but with shallow imaging, 
    for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), 
    or with deeper imaging but much smaller sample sizes (e.g \citealt{Gonzalez2005, 
    Capaccioli2015}). 
    In this paper, we take advantage of new high-quality (median seeing of
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive 
    galaxies out to 100 kpc. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    ideal for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

 %       With the help of reliable spectroscopic and photometric redshift 
 %   (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
 %   we select a large sample (${\sim} 7000$) of massive central galaxies at 
 %   $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

@@

    % In practice, reliable isolation of a physically meaningful ICL component using 
    % photometry alone is extremely difficult, if not impossible. 
    % More importantly, the majority of massive galaxies in our samples are not considered 
    % as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
    % Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
    % massive clusters where the strongest photometric evidence of an ICL component is 
    % often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
    % Burke2015}). 
    % The virgo cluster is a good  local analog of the typical galaxy in our sample.

    % Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
    % 100 kpc, while the ICL only becomes important outside that radius and is dominated 
    % by many individual tidal features (e.g. \citealt{Mihos2016}).
    % Therefore, it is highly unlikely that out main results are driven by the ICL 
    % component.

    % At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
    % galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
    % Although the rising stellar velocity dispersion in the outskirt of massive BCG
    % has been used as evidence of a kinematically separated ICL component (e.g. 
    % \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
    % we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
    % an integrated component. 
    % They both carry important information regarding the assembly of central galaxy 
    % and its dark matter halo. 
    % In recent years, we can start to investigate the origin and evolution of ICL using 
    % simulations where physical separation of ICL is possible
    % (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
    % Harris2017}). 
    % It will be interesting to perform detailed comparisons between these simulations 
    % and deep HSC observations to look into the contributions from different stellar 
    % components to the halo of massive galaxy.

@@

    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
    Miyazaki in~prep.), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 110$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
    (Please see Table 3 in \citealt{HSC_DR1} for detailed comparison).

@@

    The full details of the HSC data processing can be found in \citet{Bosch2017}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
    photometry which means that it can accurately measure both the 
    \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad flux cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
    We therefore perform an initial conservative selection of massive galaxies
    with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. 
    We also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in $i$-band as defined in \citet{HSC_DR1}.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

@@

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flags from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see \S~4.4.2 of \citet{HSC_DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

@@

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to either the uncertainty in the background 
    subtraction or the unmasked flux from other objects.
    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
    This is a conservative choice but already enables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    For more technical details of the \texttt{Ellipse} procedure, please see 
    Appendix~\ref{app:ellipse}.

@@

    We cannot extract reliable 1-D profiles for a small fraction of massive galaxies 
    because they are heavily masked out for either physical 
    (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    We visually examine the 3-color images of randomly selected galaxies with failed 
    1-D profiles.  
    Most of them are relative small galaxies that are severely contaminated by nearby 
    objects, and will not affect the results of this work.  
    Meanwhile, it is worth noting that this does exclude most major merging systems 
    among massive galaxies.

@@

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipe}).

    \texttt{iSEDFit} takes a simplified Bayesian approach. 
    In short, it first generates a large grid of SEDs from synthetic stellar 
    population models by drawing randomly from the prior distributions of relevant
    parameters (e.g. age, metallicity, dust extinction, and star formation history).
    Based on these models, it uses the observed photometry and redshift to compute 
    the statistical likelihood, and generates the posterior probability distribution 
    functions (PDF) for each parameter.  
    To get the best estimate of a given parameter, \texttt{iSEDFit} integrates the 
    full PDF over all the other nuisance parameters.
    Then, the median value and the 1-$\sigma$ uncertainty are derived based on the 
    marginalized PDF. 
    Please refer to \citet{Moustakas13} for technical details.

@@

	With \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  
	create a sample of massive central galaxies. 
	The ``central'' galaxy is defined as the galaxy that lives in the 
	center of its own dark matter halo.  
	In contrast, a galaxy in a sub-halo that is orbiting within the virial radius of a 
	more massive halo is referred to as a ``satellite''. 
	To better understand the connection between the structures of massive 
	galaxies and the assembly history of both their stars and dark matter halos, we 
	wish to focus on central galaxies in this work.

@@

        \item The SMF derived from a SDSS-\textit{GALEX} sample of $z{\sim} 0.1$ 
            galaxies by \citet{Moustakas13}. 
            Total luminosities in \citet{Moustakas13} are based on SDSS \cmodel{} 
            magnitudes. 
            They use a \m2l{} that is derived via SED fitting using \texttt{iSEDfit} 
            with similar assumptions as the ones adopted here.

>>>>

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\rachel}[1]{\textcolor{cyan}{\textbf{[Rachel: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

    \song{
    The stellar halo of massive galaxy can extend to several hundreds of kilo 
    parsecs and provide important fossil record of galaxy assembly.
    Using the wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) images 
    from the Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP), we study 
    the stellar halos of a sample of $\sim7000$ massive galaxies at 
    $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$ by tracing their  
    surface mass density profiles to 100 kpc individually. 
    The stellar halo of massive galaxy exhibit higher intrinsic diversity in their 
    outer surface density profile and higher ellipticity than the inner region. 
    We find that more massive galaxy on average shows more prominent outer stellar 
    halo with shallower surface density profiles.
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients.
    }
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at late times from a series of merging events.
    \song{
    These results also emphasize the importance of accounting for the the extended 
    stellar halos of massive galaxies when estimating their stellar masses. 
    Shallow image or inadequate profile model often leads to significantly 
    underestimated masses.
    We provide surface mass surface mass density profiles to facilitate comparisons 
    with predictions from hydrodynamic simulations and other observations.
    }

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the depth and imaging quality of SDSS and the HSC wide 
            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
            %This added depth is critical in order map the outskirts of ETGs out to 
            %large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \song{
    Massive early-type galaxies (ETGs) are predicted to assemble according to a 
    ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}): A rapid growth phase at high-redshift that 
    is dominated by intense dissipative \textit{in situ} star formation (e.g.
    \citealt{Hopkins2008, Dekel2009}), and a second phase that 
    is driven by non-dissipative processes such as dry mergers 
    (e.g. \citealt{Naab2006, Khochfar2006}), especially the minor ones 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and semi-analytic models 
    (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
    mass accreted in the second phase (\textit{ex situ} component) should increase 
    with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    }
    For instance, recent results from the 
    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at 
    \logms{}$>11.5$ (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
    does not reproduce the observed stellar mass function at high \mstar{} end.}. 
%% ------------------------------------------------------------------------------------ %%

    \song{
    Given the success of the ``two-phase'' scenario in explaining the properties of 
    high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
    vandeSande2011, Belli2014}) and the dramatic increase of their effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Newman2012, vdWel2014}), it is time to confront 
    this model with additional observations, in particular, the detailed surface 
    mass density profiles of low redshift massive galaxies. 
    }
    Early studies based on one-dimensional light profiles found that the surface 
    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
    (e.g. \citealt{Kormendy2009}; except for the most central region) and that the 
    \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). 
    However, recently, detailed empirical comparison of surface brightness profiles 
    revealed a more complicated situation showing that ETGs belong to two families, 
    those that follow single-\ser{} law, versus those that significantly deviate from 
    the single-\ser{} profile \citep{Schombert2015}.  
    Two-dimensional analyses have also found that the stellar distributions of massive 
    ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  
    \citet{Huang2013b} further suggest a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and 
    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    \song{
    Until now, deep \mden{} profiles of massive galaxies are rarely available. 
    Even in the nearby universe, it is not trivial to map the low surface
    brightness outskirts of massive galaxies (e.g., 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
    Some of these measurements are based on image stacking method (e.g. 
    \citealt{Tal2011, dSouza2015}) that suffers from several systematics. 
    The number of very massive galaxies is also very limited in the local universe.
    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
    luminosity) within 108 Mpc.
    }

    \song{
    Besides the mass density profiles, the radial profile of ellipticity also 
    contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
    Tremblay1996, Chang2013, RodriguezPadilla2013, Mitsuda2017}) and kinematics 
    (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies. 
    The elliptical profiles of massive galaxies have not been carefully studied 
    out to large radius except for few works using either image stacking method
    (e.g. \citealt{Tal2011, dSouza2015}) or small sample of nearby galaxies 
    (e.g. \citealt{Spavone2017}). 
    }

    \song{
    In this paper, we take advantage of the high--quality and deep images from the 
    Hyper Suprime-Cam (HSC) Subaru Strategic Program \citep[SSP,][]{HSC-DR1} 
    (see \S~\ref{ssec:hsc} for details) to characterize the light profiles of 
    massive galaxies out to 100 kpc. 
    }
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

@@

@@

    The Subaru Strategic Program (SSP, \citealt{HSC-SSP, HSC-DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
    Miyazaki in~prep.), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 110$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).
    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
    (Please see Table 3 in \citealt{HSC-DR1} for detailed comparison).

@@

    The full details of the HSC data processing can be found in \citet{HSC-PIPE}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{HSC-PIPE}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
    photometry which means that it can accurately measure both the 
    \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the total flux of massive ETGs (this is discussed further in 
    \citealt{HSC-PIPE}).   
    For these reasons, our results will be based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad flux cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
    We therefore perform an initial conservative selection of massive galaxies
    with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. 
    We also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in $i$-band as defined in \citet{HSC-DR1}.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

@@

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSS-DR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flags from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see \S~4.4.2 of \citet{HSC-DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

@@

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to either the uncertainty in the background 
    subtraction or the unmasked flux from other objects.
    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
    This is a conservative choice but already enables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    \song{
    The 1-D method fails to extract profiles for ${\sim}10$\% of the sample due 
    to severe contamination of other objects, they are excluded from the analysis.
    }
    For more technical details of the \texttt{Ellipse} procedure, please see 
    Appendix~\ref{app:ellipse}.

@@

@@

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    \song{
    \texttt{iSEDFit} uses a simplified Bayesian approach to estimate the 
    posterior probability distribution functions (PDF) of key stellar population
    parameters.
    }
    Although \cmodel{} tends to underestimate the total fluxes of bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipe}).

@@

@@

        \item \song{
            The SMF for SDSS-\textit{GALEX} sample at $z{\sim} 0.1$ using SDSS \cmodel{}
            photometry and \texttt{iSEDfit} stellar mass based on similar assumptions 
            (see \citet{Moustakas13} for details). 
            }
